Understanding the Landscape of Childlessness in the U.S.: A Data-Driven Exploration (1972-2022)

### 2024-03-14 outputs/paper/paper.qmd
New Average graphs added for the result section

#### Load data ####
table_nochild_age <-
  read_csv(
    file = "../data/clean_data_age.csv",
    show_col_types = FALSE
  )

table_nochild_class <-
  read_csv(
    file = "../data/clean_data_class.csv",
    show_col_types = FALSE
  )

table_nochild_degree <-
  read_csv(
    file = "../data/clean_data_degree.csv",
    show_col_types = FALSE
  )

table_nochild_sex <-
  read_csv(
    file = "../data/clean_data_sex.csv",
    show_col_types = FALSE
  )

table_nochild_marital <-
  read_csv(
    file = "../data/clean_data_marital.csv",
    show_col_types = FALSE
  )

table_nochild_health <-
  read_csv(
    file = "../data/clean_data_health.csv",
    show_col_types = FALSE
  )

@@

nochild_age_data_long <- tidyr::pivot_longer(table_nochild_age, -Age, names_to = "year", values_to = "percentage")

ggplot(nochild_age_data_long, aes(x = as.integer(year), y = percentage, color = Age)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Age Group", color = "Age Group") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long <- pivot_longer(table_nochild_class, -`Class Identification`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long$Year <- as.integer(data_long$Year)

# Plot the data
ggplot(data_long, aes(x = Year, y = Percentage, color = `Class Identification`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Class", color = "Breakdown Category") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long <- pivot_longer(table_nochild_degree, -`Degree`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long$Year <- as.integer(data_long$Year)

# Plot the data
ggplot(data_long, aes(x = Year, y = Percentage, color = `Degree`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Degree", color = "Degree") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long <- pivot_longer(table_nochild_sex, -`Gender`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long$Year <- as.integer(data_long$Year)

# Plot the data
ggplot(data_long, aes(x = Year, y = Percentage, color = `Gender`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Gender", color = "Gender") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long <- pivot_longer(table_nochild_health, -`Condition of health`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long$Year <- as.integer(data_long$Year)

# Plot the data
ggplot(data_long, aes(x = Year, y = Percentage, color = `Condition of health`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Health", color = "Condition of health") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long <- pivot_longer(table_nochild_marital, -`Marital status`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long$Year <- as.integer(data_long$Year)

# Plot the data
ggplot(data_long, aes(x = Year, y = Percentage, color = `Marital status`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Marital Status", color = "Marital status") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

>>>>

#### Load data ####
table_nochild_age <- read_csv(file = "../data/clean_data_age.csv",show_col_types = FALSE)

table_nochild_class <- read_csv(file = "../data/clean_data_class.csv",show_col_types = FALSE)

table_nochild_degree <- read_csv(file = "../data/clean_data_degree.csv",show_col_types = FALSE)

table_nochild_sex <- read_csv(file = "../data/clean_data_sex.csv",show_col_types = FALSE)

table_nochild_marital <- read_csv(file = "../data/clean_data_marital.csv",show_col_types = FALSE)

table_nochild_health <- read_csv(file = "../data/clean_data_health.csv",show_col_types = FALSE)

@@

data_long_age <- tidyr::pivot_longer(table_nochild_age, -Age, names_to = "year", values_to = "percentage")

ggplot(data_long_age, aes(x = as.integer(year), y = percentage, color = Age)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Age Group", color = "Age Group") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long_class <- pivot_longer(table_nochild_class, -`Class Identification`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long_class$Year <- as.integer(data_long_class$Year)

# Plot the data
ggplot(data_long_class, aes(x = Year, y = Percentage, color = `Class Identification`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Class", color = "Breakdown Category") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long_degree <- pivot_longer(table_nochild_degree, -`Degree`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long_degree$Year <- as.integer(data_long_degree$Year)

# Plot the data
ggplot(data_long_degree, aes(x = Year, y = Percentage, color = `Degree`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Degree", color = "Degree") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long_sex <- pivot_longer(table_nochild_sex, -`Gender`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long_sex$Year <- as.integer(data_long_sex$Year)

# Plot the data
ggplot(data_long_sex, aes(x = Year, y = Percentage, color = `Gender`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Gender", color = "Gender") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long_health <- pivot_longer(table_nochild_health, -`Condition of health`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long_health$Year <- as.integer(data_long_health$Year)

# Plot the data
ggplot(data_long_health, aes(x = Year, y = Percentage, color = `Condition of health`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Health", color = "Condition of health") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

# Pivot the data from wide to long format
data_long_marital <- pivot_longer(table_nochild_marital, -`Marital status`, names_to = "Year", values_to = "Percentage")

# Convert Year column to integer
data_long_marital$Year <- as.integer(data_long_marital$Year)

# Plot the data
ggplot(data_long_marital, aes(x = Year, y = Percentage, color = `Marital status`)) +
  geom_line() +
  geom_smooth(method = "loess", se = FALSE, linetype = "dashed", size = 1.2) +  # Add running average trend line
  labs(x = "Year", y = "Percentage of Population", title = "Childless Percentage of Population over Time by Marital Status", color = "Marital status") +
  theme_minimal() +
  theme(text = element_text(size = 10))

@@

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-nochild-avg-marital
#| fig-cap: "Average Childless Percentage of Population over Time by Marital Status"

# Group the data by Year and calculate the average of Percentage for each year
avg_data <- data_long_marital |>
  group_by(Year) |>
  summarise(Sum_Percentage = sum(Percentage, na.rm = TRUE)) |>
  mutate(avg_Percentage = Sum_Percentage / 5)

# Print the average data
# print(avg_data)

# Plot the data
ggplot(avg_data, aes(x = Year, y = avg_Percentage)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Average Percentage of Population", title = "Average Childless Percentage of Population over Time by Marital Status") +
  theme_minimal()

```
```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-nochild-avg-class
#| fig-cap: "Average Percentage Childless over Time by Class"

# Group the data by Year and calculate the average of Percentage for each year
avg_data <- data_long_class |>
  group_by(Year) |>
  summarise(Sum_Percentage = sum(Percentage, na.rm = TRUE)) |>
  mutate(avg_Percentage = Sum_Percentage / 4)

# Print the average data
# print(avg_data)

# Plot the data
ggplot(avg_data, aes(x = Year, y = avg_Percentage)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Average Percentage of Population", title = "Average Percentage Childless over Time by Class") +
  theme_minimal()

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-nochild-avg-gender
#| fig-cap: "Average Percentage Childless over Time by Gender"

# Group the data by Year and calculate the average of Percentage for each year
avg_data <- data_long_sex |>
  group_by(Year) |>
  summarise(Sum_Percentage = sum(Percentage, na.rm = TRUE)) |>
  mutate(avg_Percentage = Sum_Percentage / 2)

# Print the average data
# print(avg_data)

# Plot the data
ggplot(avg_data, aes(x = Year, y = avg_Percentage)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Average Percentage of Population", title = "Average Percentage Childless over Time by Gender") +
  theme_minimal()

```{r}
#| echo: false
#| include: true
#| warning: false
#| label: fig-nochild-avg-degree
#| fig-cap: "Average Percentage Childless over Time by Degree"

# Group the data by Year and calculate the average of Percentage for each year
avg_data <- data_long_degree |>
  group_by(Year) |>
  summarise(Sum_Percentage = sum(Percentage, na.rm = TRUE)) |>
  mutate(avg_Percentage = Sum_Percentage / 3)

# Print the average data
# print(avg_data)

# Plot the data
ggplot(avg_data, aes(x = Year, y = avg_Percentage)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Average Percentage of Population", title = "Average Percentage Childless over Time by Degree") +
  theme_minimal()
